\ifpublic{}
  % Nothing.
\else
  \input{info.tex}
\fi

\cvsection{Awards}

\cvachievement{\faUniversalAccess}{CSE Service Award for Excellence in Climate and DEI}{In April 2023}

\cvachievement{\faFile}{Best poster award, NLP@Michigan Day}{In May 2022}

\cvachievement{\faCommentO}{\nth{1} place in TASS 2017, Task 1, corpus GralTASS 1k}{SEPLN 2017. Sentiment Analysis contest. We also finished \nth{2} in one of the other two corpora.}

\cvachievement{\faFileTextO}{\nth{3} place in the Engineering Fair (``Ingeniería deMuestra'')}{CS Thesis Contest. October 2015.}

\cvachievement{\faLaptop}{\nth{1} place in National Microsoft Hoshimi Programming Contest}{In December 2009}

\cvachievement{\faSuperscript}{Finalist in National Math Olympiads}{In December 2003}

\cvsection{Grants \& Scholarships}

\cvachievement{\faFlask}{Research Initiation Grant}{By CSIC, for a project on the study of Subjectivity and its application to Humor Classification using DL.\@ \$16,632. November 2017.}

\cvachievement{\faFlask}{Research Initiation Scholarship}{By ANII, for the undergraduate thesis project. \$2,400. August 2014.}

\cvsection{Teaching}

\cvsmallevent{Information Retrieval and Web Search}{University of Michigan}{H1 2021}{}

\cvsmallevent{Advanced Data Structures and Algorithms (``Programación 3'')}{Universidad de la República}{H2 2014--2018}{}

\cvsmallevent{Logic Programming}{Universidad de la República}{H1 2016--2017}{}

\cvsmallevent{Data Structures and Algorithms (``Programación 2'')}{Universidad de la República}{H1 2014--2015, 2018}{}

\cvsection{Thesis Supervisions}

\cvsmallevent{Machine Classifier System of Answers According to their Relevance (``Sistema clasificador
automático de respuestas según relevancia'')}{B.E.\ thesis, Universidad de la República}{August 2016 --- December 2017}{}
